
\setcounter{section}{0}
\setcounter{figure}{0}
\graphicspath{{./figs/}{./figs/item-ni/}}

\NewsTitle{Intelligent Machine Condition Monitoring for Cyber-Physical Systems}
\NewsAuthor{Arkadeb Ghosal, Kaushik Ravindran, Patricia Derler, Hugo A. Andrade, and Jeannie Falcon\\%alphabetical order?
National Instruments Corporation}

% Titles:

%Cybernetics for Intelligent Machine Condition Monitoring\\and Control Applications (first choice)\\ 
% Cybernetics for intelligent monitoring
% Cybernetics for intelligent machine monitoring
% Cybernetics for intelligent machine condition monitoring

% Notes about content:

% Trend on large scale distributed sensor machine monitors
% Requires: 
% 1. monitoring the condition of indivudual parts
% 2. transmiting data and calculating the condition indicators
% 3. managing deployment of large sensor nodes

% Making data available for remote viewing and analysis

% NI InsightCM is such is an enterprise level solution to such a problem/requirement

% Modern day IIoT has enabled large distributed systems with over 30,000 sensors and 10,000 nodes. 
% Given the scale we need introduce automatic monitoring, that is node and application specific.
% In the case of rotating machinery, we have large body of knowledge on analytics. 

% Cybernetics include libraries that collect "big data" across the many nodes, and the run
% analtics for indivudals nodes, acrross region and acrross full deploymnenbts. 


% \input{doc/Intro}
\input{doc/item-ni/Trends}
\input{doc/item-ni/MCM}
\input{doc/item-ni/InsightCM}
\input{doc/item-ni/Summary}

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{Gartner_IoT_2020}
Gartner Research Inc., ``The Internet of Things'',
\newblock{\em Press Release}, November 2015, \url{http://www.gartner.com/newsroom/id/3165317} .

\bibitem{SwarmAtEdgeOfCloud}
Edward A. Lee, Jan Rabaey, David Blaauw, Kevin Fu, Carlos Guestrin, Bjorn Hartmann, Roozbeh Jafari, Doug Jones, John Kubiatowicz, Vijay Kumar, Rahul Mangharam, Richard Murray, George Pappas, Kris Pister, Anthony Rowe, Alberto Sangiovanni-Vincentelli, Sanjit A. Seshia, Tajana Simunic Rosing, Ben Taskar, John Wawrzynek, David Wessel, ``The Swarm at the Edge of the Cloud'',
\newblock{\em Design \& Test}, IEEE, Volume 31, 2014.

\bibitem{NITrendWatch2016}
National Instruments, ``NI Trend Watch 2016'',
\url{http://www.ni.com/pdf/company/en/Trend_Watch_2016_Full.pdf}, accessed Jan 12th, 2016.

\bibitem{MCMHandbook}
A. Davies. ``Handbook of Condition Monitoring: Techniques and Methodology'',
\newblock{\em Springer Science \& Business Media}, 1997.
%kinda old?

\bibitem{ResarchandMarkets15}
Research and Markets, ``Machine Condition Monitoring Market by Monitoring Type, Components, Monitoring Process``,
\newblock{\em Applications, and Geography - Global Trend \& Forecast to 2020},
November 2015.

%\bibitem{MCM_NI}
%National Instruments, ``Machine Condition Monitoring Technical Library,'' %\emph{\url{http://www.ni.com/white-paper/6511/en}}, accessed Jan 12th, 2016.

\bibitem{Randall_VibrationbasedCM}
Robert Bond Randall, 
``Vibration-based Condition Monitoring: Industrial, Aerospace and Automotive Applications'', 
\newblock{\em John Wiley \& Sons}, 2011.
%Cited by 275

\bibitem{InsightCMBrochure15}
National Instruments, ``NI InsightCM\textsuperscript{TM} Enterprise for Condition Monitoring,''
\url{ftp://ftp.ni.com/pub/branches/asean/2015_05_29_insightcm.pdf}, accessed Jan 12th, 2016.

\bibitem{ni_crio}
National Instruments, ``NI Compact RIO'', \url{www.ni.com/compactrio} .

\bibitem{MCM_UC_NI}
National Instruments, ``Featured Machine Condition Monitoring Case Studies,'' \url{http://www.ni.com/white-paper/12398/en}, accessed Jan 12th, 2016.

\bibitem{dukewebsite}
Duke Energy, \url{https://www.duke-energy.com/}, accessed Jan 20th, 2016.

\bibitem{duke}
National Instruments, ``NIWeek 2014 NI InsightCM\textsuperscript{TM} Enterprise Announcement
,'' \url{http://www.ni.com/white-paper/52392/en/}, accessed Jan 20th, 2016.

% \bibitem{LITH_TCAD2013_Pan}
% D.~Z. Pan, B.~Yu, and J.-R. Gao, ``Design for manufacturing with emerging
%   nanolithography,'' \emph{IEEE Transactions on Computer-Aided Design of
%   Integrated Circuits and Systems (TCAD)}, vol.~32, no.~10, pp. 1453--1472,
%   2013.

% \bibitem{CELL_SPIE2013_Smayling}
% M.~C. Smayling, ``{1D} design style implications for mask making and {CEBL},''
%   in \emph{Proceedings of SPIE}, vol. 8880, 2013.

% \bibitem{LITH_SPIE2014_Liebmann}
% L.~Liebmann, V.~Gerousis, P.~Gutwin, M.~Zhang, G.~Han, and B.~Cline,
%   ``Demonstrating production quality multiple exposure patterning aware routing
%   for the 10nm node,'' in \emph{Proceedings of SPIE}, vol. 9053, 2014.

\end{thebibliography}



